---
title: "STA2453H1Y - Data Science Methods, Collaboration, and Communication"
subtitle: "Course documents"
output:
  html_document:
    theme: cosmo
    highlight: textmate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Class 1 - September 11

[Data Analysis Examples](sta2453-11sept2018-class1_updatedFeb122019.html)

[In-class assignment](sta2453_inclassassign.slides-2.html)

# Class 2 - September 25

[My solution to previous in-class assignment](kidneystones_ver1-2.html)

[Project #1 Description](sta2453_2018_project1.html)

[Project #1 Draft Proposal Expectations](project1proposal.html)

[Data Analysis as Art](sta2453-class2-slides-Sept25.html)

[In-class Assignment](sta2453_class2_2018air_pollution_eda_student.html)

# Class 3 - October 9

[Statistics bootcamp - Logistic regression](logreg_slides.html) with [RMarkdown source](logreg_slides.Rmd)

# Instructions for Submitting Project #1

Detailed instructions are available [here](project1submission.html). 

# Project #2 Proposals

[Instructions](project2.html) for project #2 proposals.

# Class - January 22

[Slides](sta2453_jan22.pdf)

# Class - February 5

[Draft presentation for project #2](Project2draftpres.html)

# Class - April 2

Final Presentations.  

- Presentations should be approximately 15 minutes.

- All group members should give part of the presentation.

- Presentations will be graded using the following rubric.

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
pres_rub <- read_csv("presentation_rubric.csv")
knitr::kable(pres_rub)
```

